Summary Statistics

### 2025-02-06 extensive_tests/draft-sumstat-vignette.Rmd
Updating git in order to pull
Updating Rmd file for archipelago definition
Updating summary statistics state for mean sd of frequencies per structure type and mean correlation of a central segment of methylation states per structure type

\[
\sigma_{t}(x)=\sqrt{\frac{1}{I-1}\sum_{i=1}^{I}(x_{i,t}-\overline{x_{.,t}})^2} \\
\sigma_{t}(y)=\sqrt{\frac{1}{J-1}\sum_{j=1}^{J}(y_{i,t}-\overline{y_{.,t}})^2}
\]

@@

\[
\overline{x_{.,t}}=\frac{1}{I}\sum_{i=1}^{I}x_{i,t} \\
\overline{y_{.,t}}=\frac{1}{J}\sum_{j=1}^{J}x_{j,t}
\]

@@

\[
\hat{\sigma}(x)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(x) \\
\hat{\sigma}(y)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(y) \\
\]

@@

\[
\sigma_{t}(w)=\sqrt{\frac{1}{I-1}\sum_{i=1}^{I}(x_{i,t}-\overline{x_{.,t}})^2} \\
\sigma_{t}(z)=\sqrt{\frac{1}{J-1}\sum_{j=1}^{J}(y_{i,t}-\overline{y_{.,t}})^2}
\]

@@

\[
\overline{w_{.,t}}=\frac{1}{I}\sum_{i=1}^{I}w_{i,t} \\
\overline{z_{.,t}}=\frac{1}{J}\sum_{j=1}^{J}z_{j,t}
\]

@@

\[
\hat{\sigma}(w)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(w) \\
\hat{\sigma}(z)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(z) \\
\]

@@

# Mean correlation of a segment of methylation states per genomic structure type

@@

NOTE: Summary statistics related with tree cherries require a tree with tip labels as:

>>>>

$$
\sigma_{t}(x)=\sqrt{\frac{1}{I-1}\sum_{i=1}^{I}(x_{i,t}-\overline{x_{.,t}})^2} \\
\sigma_{t}(y)=\sqrt{\frac{1}{J-1}\sum_{j=1}^{J}(y_{i,t}-\overline{y_{.,t}})^2}
$$

@@

$$
\overline{x_{.,t}}=\frac{1}{I}\sum_{i=1}^{I}x_{i,t} \\
\overline{y_{.,t}}=\frac{1}{J}\sum_{j=1}^{J}x_{j,t}
$$

@@

$$
\hat{\sigma}(x)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(x) \\
\hat{\sigma}(y)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(y) \\
$$

@@

$$
\sigma_{t}(w)=\sqrt{\frac{1}{I-1}\sum_{i=1}^{I}(x_{i,t}-\overline{x_{.,t}})^2} \\
\sigma_{t}(z)=\sqrt{\frac{1}{J-1}\sum_{j=1}^{J}(y_{i,t}-\overline{y_{.,t}})^2}
$$

@@

$$
\overline{w_{.,t}}=\frac{1}{I}\sum_{i=1}^{I}w_{i,t} \\
\overline{z_{.,t}}=\frac{1}{J}\sum_{j=1}^{J}z_{j,t}
$$

@@

$$
\hat{\sigma}(w)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(w) \\
\hat{\sigma}(z)=\frac{1}{T}\sum_{t=1}^{T}\sigma_t(z) \\
$$

@@

# Mean correlation of a central segment of methylation states per genomic structure type

@@

NOTE: Summary statistics related with tree cherries require a tree with tip labels givenas numeric values
